Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/appendix.tex
adding small part in intro about verification

If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario. We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges. We argue that \sysname is correct by breaking down the claim:

>>>>

%If \sysname compiles a user policy to a distributed implementation, then that distributed implementation faithfully meets the centralized policy's semantics under any failure scenario. We are primarily concerned with the steady state: that is, what happens after (if) the routing protocol converges. We argue that \sysname is correct by breaking down the claim:

### 2016-01-29 paper/introduction.tex
adding small part in intro about verification

>>>>

Verification tools for network configurations~\cite{batfish} have been developed as a complimentary approach for reducing misconfigurations by checking that the low-level configurations match high-level operator intent. However, existing verification tools have their drawbacks: like templates, they do not help operators come up with the configuration in the first place, and moreover, they can only check correctness under concrete environment and failure scenarios, rather than under all possible environments and failure scenarios.
